\todoDany{Approve or change: } Reconstructing Rearrangement Phylogenies

### 2023-10-19 docs/manuscript/main.tex
Include ILP into text. TODO: Descriptions of the ILP, fix inconsistencies of variables.

\begin{document}
%
\title{Reconstructing Rearrangement Phylogenies}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

@@

\section{Introduction}
\section{Background}
\subsection{Problem Formulation}
\section{A new Method}
\subsection{Pre-selecting Adjacencies}
\todoDany{Describe Process}
\subsection{A New ILP Formulation}
\todoLeo{ILP goes here}

@@

\nocite{DOE-CHA-2021}
\nocite{BOH-BRA-DOE-STO-2021}
\subsubsection{Acknowledgements} Please place your acknowledgments at
the end of the paper, preceded by an unnumbered run-in heading (i.e.
3rd-level heading).

>>>>

\begin{document}
%
\title{\todoDany{Approve or change: } Reconstructing Rearrangement Phylogenies}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\todo{Authors and order? $\rightarrow$ until Oct 23rd.}
\begin{abstract}
\todo{We have to submit this until Oct 23rd.}

@@

\section{Introduction}
\section{Background}
\subsection{Problem Formulation}
\section{A new Method}
\subsection{Pre-selecting Adjacencies}
\todoDany{Describe Process}
\subsection{A New ILP Formulation}
\todoLeo{ILP goes here}
\todoLeo{Remove idx stuff and bring back $v_i$ notation}

\begin{algorithm}
\caption{Capping-free Small Parsimony}
\textbf{Objective}

\newcommand{\idx}{\texttt{ix}}
\hspace{0.5cm}\texttt{Maximize}
\begin{equation*}
    \alpha \sum_{\edt\in\tree} f_\edt + .... \text{\todoDany{Optimization of other factors goes here.}}
\end{equation*}

\textbf{For each tree edge $(\A,\B):=\edt\in \tree$ with $\pcmrd(\A,\B) = (\vertices\cup\pseudocaps, \adjacencyedges \cup \extremityedges \cup \selfedges)$:}

\begin{constraints}
\begin{tabular}{lcl}
	\cns & $f_\edt = n_\edt - c_\edt + q_\edt + s_\edt$\\
	\cns & $n_\edt = 0.5 \sum_{e \in \extremityedges} x_{e}$\\
    \cns & $c_\edt = \sum_{v\in \vertices} r^c_{v}$\\
    \cns & $2q_\edt \geq p^{a\trans b}+ p^{ABa} + p^{ABb} - p^{A\trans B} $\\
    \cns & $p^{a\trans b} = \sum_{v \in \vertices}r^{a\trans b}_{v}$\\
    \cns & $p^{A\trans b} = \sum_{v \in \pseudocaps^A} r^{A\trans b}_e$\\
    \cns & $p^{B\trans a} = \sum_{v\in \pseudocaps^B} r^{B\trans a}_e$\\
    \cns & $p^{A\cis a} = \sum_{v \in \pseudocaps^A} r^{A\cis a}_e$\\
    \cns & $p^{B\cis b} = \sum_{e \in \pseudocaps^B} r^{B\cis b}_e$\\
    \cns & $p^{ABa} \geq p^{B\trans a}$\\
    \cns & $p^{ABa} \geq p^{A\cis a}$\\
    \cns & $p^{ABb} \geq p^{B\cis b}$\\
    \cns & $p^{ABb} \geq p^{A\trans b}$\\
    \cns & $p^{A\trans B} = \sum_{v\in \pseudocaps^A} r^{A\trans B}_v$\\
    \cns & $s_\edt = \sum_{v\in\vertices} r^{s}_{v}$ \\
    (\ref{ilp:slmstart}) to (\ref{ilp:slmend})& Shao-Lin-Moret~\cite{SHA-LIN-MOR-2015} constraints& -- see Table~\ref{tab:slmcons}\\
    (\ref{ilp:regvstart}) to (\ref{ilp:regvend})& Reporting for regular vertices& -- see Table~\ref{tab:regv}\\
    (\ref{ilp:pcstart}) to (\ref{ilp:pcend})& Reporting for \gls{pcaps}& -- see Table~\ref{tab:pcaps}\\
    (\ref{ilp:csstart}) to (\ref{ilp:csend})& Reporting circular singletons& --  see Table~\ref{tab:csreport}\\    
\end{tabular}

\end{constraints}
\todoLeo{Put domains here?}
\todoLeo{Fix formatting}
\end{algorithm}

\newcommand{\idx}{}
\begin{table}

\begin{constraints}
\caption{Shao-Lin-Moret constraints.} \label{tab:slmcons}
\begin{tabular}{lcl}
 \cns\label{ilp:slmstart} & $\sum_{uv\in \ades} x_{e} = 1 $ & $\forall u\in \vertices$\\
     \cns & $\sum_{uv\in E_{ext} \cup E_{id} } x_{uv}= 1$ & $\forall u\in \vertices$  \\
     \cns & $x_e=x_d$ & for all sibling edges $e,d$\\
     \cns & $y_v + \idx{u}(1-x_{uv}) \geq y_u$ &$\forall uv \in \adjacencyedges\cup \extremityedges$\\
          & $\idx{u}(1-x_{uv})\geq y_u$& $\forall uv \in \selfedges$\\
    \cns\label{ilp:slmend} & $\idx{v}z_v \leq y_v$ & $\forall v\in \vertices\cup\pseudocaps $\\
\end{tabular}
\end{constraints}

\end{table}

\begin{table}

\begin{constraints}
\caption{Reporting for regular vertices.\comment{This is basically exactly the same as in ding, just swap out $r^{ab}$ for $t$ and $\parityvar$ for $r$ and root reports on vertices instead of edges.}} \label{tab:regv}
\begin{tabular}{lcl}
\cns\label{ilp:regvstart} & $\parityvar^\edt_v \leq 1 - x_{uv}$ & $\forall uv \in \selfedges^\A$\\
     & $\parityvar^\edt_v \geq  x_{uv}$ & $\forall uv \in \selfedges^\B$\\
\cns & $\parityvar_v \leq \parityvar_u +  (1-x_{uv})$& $\forall uv \in \extremityedges$\\
& $\parityvar_u \leq \parityvar_v + r_{uv}^{a\trans b} + (1-x_{uv})$& $\forall uv\in E_{adj}^\A,u,v\notin \pseudocaps$\\
& $\parityvar_u \leq \parityvar_v + (1-x_{uv})$& $\forall uv\in E_{adj}^\B,u,v\notin \pseudocaps$\\

\cns & $r_{v}^c \leq z_v$&$\forall v \in \vertices^\A$\\
\cns\label{ilp:regvend} & $r_{u}^{a\trans b} \leq x_{uv}$&$\forall uv\in\selfedges^\A$\\
\end{tabular}
\end{constraints}

\end{table}

\begin{table}

\begin{constraints}
\caption{Reporting for \gls{pcaps}.} \label{tab:pcaps}
\begin{tabular}{lcl}
\cns\label{ilp:pcstart} & $\parityvar_v = 0$ & $\forall v \in \pseudocaps^\A$\\
 & $\parityvar_v = 1$ & $\forall v \in \pseudocaps^\B$\\
\cns & $\parityvar_u \leq \parityvar_v + r_{v}^{A\trans B} + r_{v}^{A\trans b} + (1-x_{uv})$& $\forall uv\in \ades, v \in \pseudocaps^\A$\\
    & $\parityvar_u \leq \parityvar_v + r_{u}^{B\trans a} + (1-x_{uv})$& $\forall uv\in \ades, u\in \pseudocaps^\B$\\
    \cns & $r_{v}^{A\trans B} \leq z_v$&$\forall v \in \pseudocaps^\A$\\
    \cns & $1 -y_v \leq r^{A\trans b}_{v} + r^{A\cis a}_v$ & $v \in \pseudocaps^\A$\\
        & $1 -y_v \leq r^{B\trans a}_{v} + r^{B\cis b}_v$ & $v \in \pseudocaps^\B$\\
    \cns & $y_{v_i} \leq i(1-r_{v}^{R})$&$v\in \pseudocaps^\A,R\in  \{A\trans b, A\cis a\}$\\
     & $y_{v_i} \leq i(1-r_{v}^{R})$&$v\in \pseudocaps^\B,R\in  \{B\trans a, B\cis b\}$\\
    \cns\label{ilp:pcend} & $r_{v}^{A\trans B} \leq b_u$&$\forall uv\in \adjacencyedges, v \in \pseudocaps^A$ \\
    & $r_{v}^{A\trans b} \leq b_u$&$\forall uv\in \adjacencyedges, v \in \pseudocaps^A$ \\
    & $r_{v}^{B\trans a} \leq 1-b_u$&$\forall uv\in \adjacencyedges, v \in \pseudocaps^\B$\\
\end{tabular}
\end{constraints}

\end{table}

\begin{table} \caption{Reporting circular singletons.\comment{(This is what we developed last week.)}}\label{tab:csreport}
\begin{tabular}{lcl}
     \cns\label{ilp:csstart} & $d_u+d_v + x_{uv}\leq 2$ & $\forall uv \in \adjacencyedges\cup \selfedges$  \\
     & $d_u + d_v - x_{uv} \geq 0$ & $\forall uv \in \adjacencyedges\cup \selfedges$  \\
    \cns & $w_u = w_v$ & $\forall uv \in \selfedges$\\
    \cns\label{ilp:csend} &$K (1- x_{uv} + r^{s}_{u} + r^{s}_{v}) + w_v \geq w_u + d_v - d_u $ & $\forall uv\in \adjacencyedges$\\
     %& $K (1- x_{uv} + r^{s}_{v} + r^{s}_{u}) + w_u \geq w_v + d_u - d_v $ & $\forall uv\in \adjacencyedges$\\
\end{tabular}
\end{table}

\todoLeo{Fix inconsistencies with comparison in $\parityvar$ and $z$.}

@@

\subsubsection{Acknowledgements} Please place your acknowledgments at
the end of the paper, preceded by an unnumbered run-in heading (i.e.
3rd-level heading).
